Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-05 manuscript/manuscript.Rmd
Several changes
- fix draw.io diagrams
- add attention section

```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/nn.png")
```

@@

While linear regression (i.e., the specific case of GLM with a gaussian distribution and identity link function) is not
commonly used for severity modeling, we throw it into the mix as a benchmark, a practice we recommend in order to
check reasonablness of other models' results. Since it is possible for a linear
regression to output negative values, we cap the predictions below by 0.01 during scoring. Somewhat surprisingly, in 
the problem we
are considering, it performs similary to the more complex neural network models in the RMSE metric (which it optimizes
for, as the unit deviance of the normal distribution correspond to MSE.) Of course, this is not to discredit neural
networks or GLMs, as the experiments are performed without extensive hyperparameter tuning or feature engineering.

@@

Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How 
should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings? Take credibility mixture over embeddings Cluster embeddings PCA of embeddings
-->
# Attention based modelling {#attention_models}

>>>>

```{r nn-1, echo = FALSE, fig.cap = "Architecture of Models 2 and 4.", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/nn.pdf")
```

@@

While linear regression (i.e., the specific case of GLM with a gaussian distribution and identity link function) is not
commonly used for severity modeling, we throw it into the mix as a benchmark, a practice we recommend in order to
check reasonableness of other models' results. Since it is possible for a linear
regression to output negative values, we cap the predictions below by 0.01 during scoring. Somewhat surprisingly, in 
the problem we
are considering, it performs similar to the more complex neural network models in the RMSE metric (which it optimizes
for, as the unit deviance of the normal distribution correspond to MSE.) Of course, this is not to discredit neural
networks or GLMs, as the experiments are performed without extensive hyperparameter tuning or feature engineering.

@@

Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How 
should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings? Take credibility mixture over embeddings Cluster embeddings PCA of embeddings
-->
# Attention based modelling {#attention_models}
In this section we investigate whether the predictive performance of the models applied to the NFIP dataset can be improved
by applying the attention based models defined in Section \ref{attention}. We discuss the implementation of each of the 
Simple Attention, TabTransformer and TabNet models in the following sub-section, then discuss how the modifications made
to the embeddings through the application of attention can be visualized in the following sub-section. We conclude the 
section with a discussion of the model results.

## Models

5. A neural network based on the design of Model 4, with an attention component
6. Similar to Model 5, a neural network implementing the TabTransformer architecture
7. A neural network implementing the TabNet architecture

Compared to the models presented in the previous section, the models presented here are closer to state of the art models that
might be used for tabular data modelling problems. To the best of our knowledge, this is the first analysis of these architectures
within the actuarial literature.

### Model 5: Simple Attention Network
Model 5 is conceptually similar to Model 4, except for the following two aspects. First, we standardize the dimension of the embedding 
layers to 8 dimensions for each categorical covariate. This is done to allow for the application of the attention component, which 
requires the embeddings for each covariate to have the same dimension. Second, we apply a self-attention mechanism within the network, 
as shown in Equation \ref{eq:embed_to_attn_to_nn}. We illustrate this architecture in Figure \@ref(fig:nn-2).

```{r nn-2, echo = FALSE, fig.cap = "Architecture of Model 5.", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/sna2.pdf")
```

### Model 6: Neural Network with Unidimensional Embeddings

### Model 7: Neural Network with Unidimensional Embeddings
